Diversity and evolution of centromere repeats in the maize genome

### 2014-07-19 centc.tex
added useles comment
n

Centromere repeats are found in most eukaryotes and play a critical role in kinetochore formation.  
Though centromere repeats exhibit considerable diversity both within and among species, little is understood about the mechanisms that drive centromere repeat evolution.  
Here, we use maize as a model to investigate how a complex history involving polyploidy, fractionation, and recent domestication has impacted the diversity of the maize centromeric repeat CentC.  
We first validate the existence of long tandem arrays of repeats in maize and other taxa in the genus \emph{Zea}.  
Although we find considerable sequence diversity among CentC copies genome-wide, genetic similarity among repeats is highest within these arrays, suggesting that tandem duplications are the primary mechanism for the generation of new copies.  
Nonetheless, clustering analyses identify similar sequences among distant repeats, and simulations suggest that this pattern may be due to homoplasious mutation.  
Although the two ancestral subgenomes of maize have contributed nearly equal numbers of centromeres, our analysis shows that the majority of all CentC repeats derive from one of the parental genomes, with a even stronger bias when examining the largest assembled contiguous clusters.  
Finally, by comparing maize with its wild progenitor teosinte, we find that the abundance of CentC likely decreased after domestication, while the pericentromeric repeat Cent4 has drastically increased.

@@

\section*{Methods} 
\label{methods}

\subsection*{CentC Repeat Identification and Diversity}

>>>>

Centromere repeats are found in most eukaryotes and play a critical role in kinetochore formation.  
Though centromere repeats exhibit considerable diversity both within and among species, little is understood about the mechanisms that drive centromere repeat evolution.  
Here, we use maize as a model to investigate how a complex history involving polyploidy, fractionation, and recent domestication has impacted the diversity of the maize centromeric repeat CentC.  
We first validate the existence of long tandem arrays of repeats in maize and other taxa in the genus \emph{Zea}.  
Although we find considerable sequence diversity among CentC copies genome-wide, genetic similarity among repeats is highest within these arrays, suggesting that tandem duplications are the primary mechanism for the generation of new copies.  
Nonetheless, clustering analyses identify similar sequences among distant repeats, and simulations suggest that this pattern may be due to homoplasious mutation.  
Although the two ancestral subgenomes of maize have contributed nearly equal numbers of centromeres, our analysis shows that the majority of all CentC repeats derive from one of the parental genomes, with an even stronger bias when examining the largest assembled contiguous clusters.  
Finally, by comparing maize with its wild progenitor teosinte, we find that the abundance of CentC likely decreased after domestication, while the pericentromeric repeat Cent4 has drastically increased.

@@

\section*{Methods} 
\label{methods}
%this is a comment
\subsection*{CentC Repeat Identification and Diversity}
